Tactic Script Optimisation for Aesop

### 2024-09-17 paper.tex
Add reference for supplement; evaluation results in intro

Concluding the paper, I evaluate the performance of script generation and the efficacy of dynamic structuring (Section~\ref{sec:evaluation}) and survey related work (Section~\ref{sec:related}).
The described optimisation pipeline is available in mainline Aesop\footnote{\url{https://github.com/leanprover-community/aesop}} and can already be used by Mathlib~\cite{Mathlib} developers and other Lean users.
The supplement for this paper\footnote{TODO} contains the exact version of Aesop described here as well as all materials needed to reproduce the evaluation.

>>>>

Concluding the paper, I evaluate the performance of script generation and the efficacy of dynamic structuring (Section~\ref{sec:evaluation}) and survey related work (Section~\ref{sec:related}).
The evaluation shows that script generation, both with static reordering and dynamic reordering, is fast enough in almost all cases.
It also shows that dynamic reordering is more effective than static reordering, though the effect is small.

The described optimisation pipeline is available in mainline Aesop\footnote{\url{https://github.com/leanprover-community/aesop}} and can already be used by contributors to Lean's mathematical library, Mathlib~\cite{Mathlib}, and other Lean users.
The supplement for this paper~\cite{supplement} contains the exact version of Aesop described here, as well as all materials needed to reproduce the evaluation.
